\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2015-06-17 paper/subdocuments/results.Rnw
update Paper and results.Rnw

#bern kantonal (liegt lokal wegen datenschutz)
try(bern_kt<-read.dta("U:/Persönlich/Forschung/Uni Bern/taxdata_BE_12.dta"))
try(bern_kt <- read.dta("G:/stick/bern/taxdata_BE_12.dta"))
#> nrow(bern_kt)
#[1] 622368
nrow(filter(bern_kt,von=="2012-01-01",bis=="2012-12-31"))
#[1] 605975 wir filtern ca. 3% unterjährige

@@

bern <- filter(bern,Satzeink_BUND<=TOTEINK,erm==0)
bern$verfeink<-bern$TOTEINK+bern$privattrans_bez-bern$steuertotal

@@

fig_bern_gini <- ggplot(bern_gini_long, aes(x=stj,y=Gini)) +
  scale_y_continuous(limits=c(0.28,0.6))+
  scale_x_continuous(breaks=number_ticks(5)) +
  geom_point(aes(shape=Income),size=4)+
  geom_line(aes(linetype=Income),size=1)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 0.3))+
  ggtitle("Gini coefficients of different income concepts")
fig_bern_gini

>>>>

#bern kantonal (liegt lokal wegen datenschutz)
try(bern_kt<-read.dta("U:/Persönlich/Forschung/Uni Bern/Steuerdaten_BE_2002_2012.dta"))
try(bern_kt <- read.dta("G:/stick/bern/taxdata_BE_12.dta"))
#> nrow(bern_kt)
#[1] 622368
nrow(filter(bern_kt,von=="2012-01-01",bis=="2012-12-31"))
#[1] 605975 wir filtern ca. 3% unterjährige

@@

bern <- filter(bern,Satzeink_KANTON<=TOTEINK,erm==0)
bern$verfeink<-bern$TOTEINK+bern$privattrans_bez-bern$steuertotal

@@

fig_bern_gini <- ggplot(bern_gini_long, aes(x=stj,y=Gini)) +
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(breaks=number_ticks(5)) +
  geom_point(aes(shape=Income),size=3)+
  geom_line(aes(linetype=Income),size=1)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 0.3))+
  ggtitle("Gini coefficients of different income concepts")
fig_bern_gini
